\pkg{digiRhythm}: an \proglang{R} package for rhythmicity assessment using the degree of functional coupling

### 2023-06-06 jstatsoft/article.Rnw
new proposal for the discussion

>>>>

\section{Discussion (New proposal Marie)}

The \pkg{digiRhythm} package presents a novel, user-friendly, and accessible tool for researchers in the field of rhythmicity, animal behavior, and beyond. The package offers a versatile approach to assessing rhythmicity based on digital activity records. By leveraging the power of \proglang{R}, it brings robust statistical capabilities and intuitive visualization features into the hands of researchers.

While the current implementation of the \pkg{digiRhythm} package focuses on rhythmicity in farm animals, the underlying principles and methodology can be extended to other organisms, including humans. This opens up exciting avenues for future research in various domains. The \pkg{digiRhythm} package enables the calculation of rhythmicity from any activity data, if the data are prepared in a suitable format.It offers the propability, to compute the rhythmicity and therefore allows to gain further insight into the organism's harmonic patterns. As further studies showed, an organism in a good physiological state will present harmonic locomotory patterns, whereas physiological events (e. g. calving in cows), physiological or psychological diseases desynchronize these rhythmic patterns. However, we have no evidence if these activity patterns are intrinsically (such as going to sleep) or extrinsically (such as waking up to an alarm) motivated. Such extrinsic factors could affect rhythmic activity patterns and blur physiological rhythmicity patterns. To date, the package provides the option to exclude extrinsically structured time spans from the analysis. However, in order to increase the understanding of rhythmicity, future studies should investigate how these extrinsic factors affect rhythmicity calculations.

The DFC calculation within the package includes a unique utilization of harmonic frequencies related to the 24-hour day, which provides a novel approach for rhythmicity analysis. However, further research is needed, to completely validate the value. These studies should evaluate how low collection frequency (currently 15 minutes) can be set to create reliable rhythmicity calculations. Additionally, the sliding seven day period, the DFC calculation depends on, and its reduction should be investigated further. Finally, the DFC should be compared with other metrics to calculate rhythmicity, as the Interdaily Stability (IS) and the Fourier-Based Approximation with Thresholding (FBAT). As well as validating the DFC, using simulated data.
